The problem and promise of scale in multilayer networks

### 2019-09-11 paper/introduction.Rmd
more box1

Spatial data can be

how associations are measured: e.g. spatsoc
how relocations are categorized: e.g. landcover

Multilayer networks incoroprate spatial variables in two ways:
1. for determining association between individuals in a social system
1. for characterizing the spatial context of social systems

For example, association between individuals can be determined using georeferenced biologging devices such as radio‐frequency identification tags, radiotelemetry, and global positioning system (GPS) devices. Proximity based social networks (PBSNs) are association networks based on close proximity between individuals [@spiegel2016].

>>>>

Spatial data can be:

* how associations are measured: e.g. spatsoc
* how relocations are categorized: e.g. landcover

Multilayer networks incoroprate spatial variables in two ways:

1. for determining association between individuals in a social system
1. for characterizing the spatial context of social systems

## Measuring association
For example, association between individuals can be determined using georeferenced biologging devices such as radio‐frequency identification tags, radiotelemetry, and global positioning system (GPS) devices.

Proximity based social networks (PBSNs) are association networks based on close proximity between individuals [@spiegel2016].

Biologging with GPS allows for simultaneous spatiotemporal sampling of multiple individuals in a group or population

## Spatial context
The spatial context of social systems can be defined as all

what is the spatial context of an animal social system

explicit spatial locations
habitat patches
landscape/habitat connectivity
social variable + home range overlap = opportunity to interact
